---
title: "Crime in San Francisco"
author: "Emiliano Olmedo"
date: "1/3/2021"
output:
  
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Subset

This dataset comes from kaggle web site <https://www.kaggle.com/roshansharma/sanfranciso-crime-dataset> and I will use it to develop a data product, as final project.We subset the dataset for 3 differents graphs, Crime type (df2), Crime in each district (df3) and most dangerous streets (df4), for the sake of visualization graph we have to give more importance to those cases that have more than 200 or 100 (n>200 or n>100)


```{r cars, echo = FALSE, comment='',warning=FALSE, message=FALSE}
library(dplyr)
library(leaflet)
library(plotly)
library(tidyr)
library(plotly)

setwd('C:\\Users\\emili\\OneDrive\\Escritorio\\R\\Coursera R\\Web App\\Map')
data <-read.csv('Police_Department_Incidents_-_Previous_Year__2016_.csv')
#data <- as_tibble(data) %>% select(IncidntNum,Category, PdDistrict,X,Y)
longitud <-data$X
latitude <- data$Y
category <- data$Category
incidntNum <- data$IncidntNum
districts <-data$PdDistrict
dayoftheweek <- data$DayOfWeek
resolution <- data$Resolution
street<- data$Address

```




```{r preprocessing,echo=TRUE}

PoliceData <- data.frame(latitude, longitud, category,incidntNum,districts,dayoftheweek,resolution,street)
FinalData <- PoliceData[complete.cases(PoliceData), ]
df <- distinct(FinalData, incidntNum, .keep_all = TRUE)
df2 <- count(df, category, sort = TRUE)
dfdistrict <- subset(df,districts !='')
df3 <- count(dfdistrict,districts,sort = TRUE)
df2 <- subset(df2,n>100)
df4<-count(df,street,sort = F)
dfsub<-subset(df4,n>200)


```
## LeafLet Map

```{r leaflet, echo=TRUE, warning=FALSE}
df[1:2000,] %>% leaflet() %>% addTiles() %>% addCircleMarkers(~longitud,~latitude,radius=3 , color="black",  fillColor="blue", stroke = TRUE, fillOpacity = 0.8, group="Blue")

```

## Crime Type



```{r leaflet1, echo=TRUE, warning=FALSE,fig.height=5, fig.width=5}
p1<-ggplot(df2, aes(x = reorder(category, -n), y = n)) + 
  geom_bar(stat="identity")+labs(title="Crime Histogram") + 
  labs(x="Crime type",y="Number of Cases")+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
(fig1<- ggplotly(p1))
```

## Amount of crime in each district

```{r leaflet2, echo=TRUE, warning=FALSE,fig.height=4, fig.width=6}
p2<-ggplot(df3, aes(x = reorder(districts, -n), y = n)) + 
  geom_bar(stat="identity",fill='blue')+labs(title="Crime Histogram") + 
  labs(x="District",y="Number of Cases")+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
(fig2<- ggplotly(p2))
```

%## Most Dangerous streets

%```{r leaflet3, echo=TRUE, warning=FALSE,fig.height=5, fig.width=6}
%p4<-ggplot(dfsub, aes(x = reorder(street, -n), y = n)) + 
%  geom_bar(stat="identity",fill ='red')+labs(title="Crime Histogram") + 
%  labs(x="Crime type",y="Number of Cases")+
%  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
%(fig4<- ggplotly(p4))

%```






